Group 1: Tennis 

### 2019-12-11 Group1Prez.Rmd
Done up until new data

```{r, echo = FALSE}

@@

>>>>

```
\pause
```{r, echo = FALSE}

@@

## Tournament Results: Women
```{r, echo=FALSE}
Tourney1_Women = data.frame(`P(Winning a Rally)` = TDWomen[,1],
                            `Paper P(Winning the Tournement)` = c(.2872, .3599, .0482, .3074))
#`Our P(Winning the Tournement )` =round( pTC(TDWomen[1,1],TDWomen[2,1],TDWomen[3,1],TDWomen[4,1], 2), 4)

rownames(Tourney1_Women)<- c("S. Williams","L. Davenport",  "A. Mauresmo", "V. Williams")

T1<- table(base::sample(rownames(Tourney1_Women), 2000, prob = Tourney1_Women$Paper.P.Winning.the.Tournement., replace = TRUE))

Winner1 <- which(T1 == max(T1))
#Winner1

#T2<- table(base::sample(rownames(Tourney1_Women), 2000, prob = Tourney1_Women$Our.P.Winning.the.Tournement., replace = TRUE)) 
#Winner2 <- which(T2 == max(T2))
#Winner2

ggplot(data.frame(T1)) +
  geom_col(aes(x=Var1, y=Freq)) +
  xlab("Players") +
  ggtitle("Which Player Won the Tournement?")

## Tournament Results: Men
```{r, echo=FALSE}
Tourney1_Men = data.frame(`P(Winning a Rally)` = TDMen[,1],
                            `Paper P(Winning the Tournement)` = c(.2872, .3599, .0482, .3074))
#`Our P(Winning the Tournement )` =round( pTC(TDMen[1,1],TDMen[2,1],TDMen[3,1],TDMen[4,1], 2), 4)

rownames(Tourney1_Men)<- c("P. Sampras","S. Schalken",  "A. Agassi", "L. Hewitt")

T1<- table(base::sample(rownames(Tourney1_Men), 2000, prob = Tourney1_Men$Paper.P.Winning.the.Tournement., replace = TRUE))

Winner1 <- which(T1 == max(T1))
#Winner1

#T2<- table(base::sample(rownames(Tourney1_Men), 2000, prob = Tourney1_Men$Our.P.Winning.the.Tournement., replace = TRUE)) 
#Winner2 <- which(T2 == max(T2))
#Winner2

ggplot(data.frame(T1)) +
  geom_col(aes(x=Var1, y=Freq)) +
  xlab("Players") +
  ggtitle("Which Player Won the Tournement?")
